A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-02-20 writeup/paper.tex

%%%%%%%%%%%%%%% SURVEY TABLE %%%%%%%%%%%
%\begin{table*}[h]
%\centering
%\begin{tabular}{lc}\hline\hline\\
%Is [HIT language/English] your native language? &3,480\\
%How many years have you spoken [HIT language]?&3,767\\
%How many years have you spoken English?&3,840\\
%What country do you live in?&3,890\\
%Current location (collected automatically)& 5,054\\
%\hline\\
%Total unique workers& 5,281\\
%\hline\hline
%\end{tabular}
%\caption{Demographic survey questions and number of Turkers with valid responses for each}
%\label{survey-tab}
%\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%% SURVEY TABLE %%%%%%%%%%%
\begin{figure}[h]
\begin{tabular}{lc}\hline\hline\\
Is [HIT language/English]&\multirow{2}{*}{3,480}\\
your native language? &\\
How many years have you&\multirow{2}{*}{3,767}\\
spoken [HIT language]?&\\
How many years have you&\multirow{2}{*}{3,840}\\
spoken English?&\\
What country do you live in?&3,890\\
Geolocation (collected automatically)& 5,054\\
\hline\\
Total workers& 5,281\\
\hline\hline
\end{tabular}
\caption{Demographic survey questions and number of Turkers with valid responses for each}
\label{survey-tab}
\end{figure}
%\begin{table*}[h]
%\centering
%\begin{tabular}{lc}\hline\hline\\
%Is [HIT language/English] your native language? &3,480\\
%How many years have you spoken [HIT language]?&3,767\\
%How many years have you spoken English?&3,840\\
%What country do you live in?&3,890\\
%Current location (collected automatically)& 5,054\\
%\hline\\
%Total unique workers& 5,281\\
%\hline\hline
%\end{tabular}
%\caption{Demographic survey questions and number of Turkers with valid responses for each}
%\label{survey-tab}
%\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
